Human Factors Influencing Visual Statistical Inference

### 2015-08-29 sociology_paper.Rnw
reference added

In experiments~4,~5 and~6, different visual test statistics were used on the same data, providing the ability to examine the effect of these choices, the use of lineup tests for comparisons and two examples are discussed in \citet{heike:2012}

>>>>

In experiments~4,~5 and~6, different visual test statistics were used on the same data, providing the ability to examine the effect of these choices, the use of lineup tests for comparisons and  examples are discussed in \citet{heike:2012, qqplots:2015}
